TEMPERATURES AND METALLICITIES FOR 10,000 M DWARFS\\ IN THE \apogee\ SURVEY

### 2018-09-19 paper/draft.tex
ref figure

Two tests of consistency were used to assess the validity of our derived test labels: (1) the self-test comparing training labels and test labels, and (2) the leave-one-out cross validation test, in which we train a model on all sources but \emph{n}, then apply the \emph{N-1} source trained model to get the labels for \emph{n}. Precision (scatter) and bias of the model for each test are calculated as the standard deviation and mean of the difference in training and test labels respectively. JB: POINT TO THESE RESULTS FOR THIS MODEL IN THE FIGURES

>>>>

Two tests of consistency were used to assess the validity of our derived test labels: (1) the self-test comparing training labels and test labels, and (2) the leave-one-out cross validation test, in which we train a model on all sources but \emph{n}, then apply the \emph{N-1} source trained model to get the labels for \emph{n}. Precision (scatter) and bias of the model for each test are calculated as the standard deviation and mean of the difference in training and test labels respectively (Figure \ref{fig:mann_validation}).
